### 2010-02-22 ChrisnaSections.tex
I think this is the beginning of a beautiful friendship.

% StatusReport.tex
% Chrisna Aing and Sarah Halls

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[hmargin=3cm, vmargin=3cm]{geometry}
\begin{document}

    \noindent{\textbf{Status Report for Otter Estimation Project \hfill Feb. 18,
    2010}

    \noindent{From: Chrisna Aing, Sarah Halls, Kiva Oken, Carleton College
    Senior Comps group} \\

    Recall that our "standard model," contains the following parameters:
    \(\psi\) (occupancy rate), \(\theta\) (probability of laying down a track,
    given occupancy), \(p\) (the detection probability for each observer; so \(1
    - p\) is the false negative rate), and \(E\) (the false positive rate for
    each observer).  We have also worked with a CAR model using the WinBUGS CAR
    installation.

    Since both our standard model and our CAR model have been working relatively
    well on our simulated data, we moved onto running them on the actual data.

    The standard model ran without convergence issues on the 2003 data for all
    rivers, but it did not converge on any of the 2004 data.  We simplified the
    model by eliminating E (assuming no false positives) in an attempt to
    improve convergence, which worked for the 402m Whitewater River and 402m 
    Zumbro River data.  Although none of the Mississippi River's 2004 data 
    converged, we are still including estimates for the 402m Mississippi River 
    data.

    The CAR model did not converge for any of the data.  Although the standard
    model and the CAR model performed similarly in testing when both models
    converged, the standard model converged much more often than the CAR model
    did.  We think this is because the CAR model attempts to estimate too many
    parameters.  There is a different estimate of \(\theta\) for every site,
    which adds a considerable amount of complexity to the model.  We also tried
    to simplify this model by eliminating E because this was somewhat successful
    with the standard model.  This improved convergence with the 402m data, but
    gave us \(\psi\) estimates greater than 0.9 for all rivers, which does not
    seem reasonable.  Therefore, we are not going to include any estimates of
    parameters from the CAR model in this report.

    We decided not to run the models on the alternating plots.  In our earlier
    analysis, we discovered that the main difference between alternating plots
    and all plots was that the alternating plots showed more independence in the
    data.  When testing the standard model on spatially dependent simulated
    data, we found that the estimates were fairly accurate.  The CAR model
    estimates were also fairly accurate on this simulated data, when it
    converged.  Therefore, we decided to use the data that includes all plots
    because we feel that having the additional information from all plots is
    more important to the model than independence is.

    All of our estimates are below and are accompanied with some thoughts about
    their convergence.  We are wondering if these estimates seem reasonable,
    based upon what you know about the three rivers. \\

    % Mississippi River!
    \begin{tabular}{|l|l|l|l|}
        \hline
        \multicolumn{4}{|l|}{\textbf{Mississippi River, 2003}} \\
        \hline
            & 402m & 804m & 1608m \\
        \hline
        \multirow{2}{*}{E[Danny]}
            & 0.01954 & 0.04808 & 0.06885 \\
            & (0.006515, 0.03663) & (0.01874, 0.08187) & (0.01778, 0.1383) \\
        \hline
        \multirow{2}{*}{E[John]}
            & 0.05216 & 0.07771 & 0.13650 \\
            & (0.027710, 0.07745) & (0.03881, 0.12100) & (0.03449, 0.2330) \\
        \hline
        \multirow{2}{*}{E[Tom]}
            & 0.02668 & 0.06140 & 0.10230 \\
            & (0.011990, 0.04622) & (0.02789, 0.10390) & (0.04287, 0.1796) \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.65240 & 0.67340 & 0.74960 \\
            & (0.548300, 0.75990) & (0.56760, 0.78290) & (0.60510, 0.8910) \\
        \hline
        \multirow{2}{*}{p[John]}
            & 0.67770 & 0.77580 & 0.82540 \\
            & (0.583500, 0.77280) & (0.66060, 0.88690) & (0.71390, 0.9326) \\
        \hline
        \multirow{2}{*}{p[Tom]}
            & 0.53670 & 0.54220 & 0.65330 \\
            & (0.501200, 0.61300) & (0.50160, 0.62850) & (0.51530, 0.8104) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.59380 & 0.69370 & 0.75820 \\
            & (0.439000, 0.75990) & (0.51800, 0.87380) & (0.54110, 0.9300) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.15280 & 0.20730 & 0.27690 \\
            & (0.111900, 0.19780) & (0.14580, 0.27390) & (0.19030, 0.3716) \\
        \hline
    \end{tabular}
    \\

    This data converged well, for the most part.  At the 1608m plot size, E,
    \(\psi\), and \(\theta\) did not converge well. \\

    \begin{tabular}{|l|l|}
        \hline
        \multicolumn{2}{|l|}{\textbf{Mississippi River, 2004}} \\
        \hline
            & 402m \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.3129 \\
            & (0.2174, 0.8107) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.7613 \\
            & (0.6609, 0.8833) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.8511 \\
            & (0.2426, 0.9973) \\
        \hline
    \end{tabular}
    \\

@@

    % Whitewater River!
    \begin{tabular}{|l|l|l|}
        \hline
        \multicolumn{3}{|l|}{\textbf{Whitewater River, 2003}} \\
        \hline
            & 402m & 804m \\
        \hline
        \multirow{2}{*}{E[Danny]}
            & 0.05608 & 0.0555 \\
            & (0.02474, 0.09554) & (0.002859, 0.1390) \\
        \hline
        \multirow{2}{*}{E[John]}
            & 0.16570 & 0.1931 \\
            & (0.10130, 0.23510) & (0.065910, 0.3384) \\
        \hline
        \multirow{2}{*}{E[Tom]}
            & 0.15350 & 0.2241 \\
            & (0.09758, 0.21660) & (0.110000, 0.3623) \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.66990 & 0.6985 \\
            & (0.56080, 0.79040) & (0.573100, 0.8366) \\
        \hline
        \multirow{2}{*}{p[John]}
            & 0.92040 & 0.9877 \\
            & (0.84270, 0.97590) & (0.945100, 1.0000) \\
        \hline
        \multirow{2}{*}{p[Tom]}
            & 0.75910 & 0.8575 \\
            & (0.65060, 0.85800) & (0.745400, 0.9600) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.87590 & 0.9126 \\
            & (0.72910, 0.98880) & (0.746900, 0.9955) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.24100 & 0.3779 \\
            & (0.17890, 0.30900) & (0.286500, 0.4721) \\
        \hline
    \end{tabular}
    \\

    While the 402m data converged well, E, \(\psi\), and \(\theta\) did not
    converge well for the 804m data. \\

    \begin{tabular}{|l|l|l|l|}
        \hline
        \multicolumn{2}{|l|}{\textbf{Whitewater River, 2004}} \\
        \hline
            & 402m \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.8237 \\
            & (0.5323, 0.9804) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.6066 \\
            & (0.4246, 0.8382) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.2068 \\
            & (0.1211, 0.3550) \\
        \hline
    \end{tabular}
    \\

    This data converged well.  However, we feel that the absence of E from the
    model makes the estimates much less dependable. \\

    % Zumbro River!
    \begin{tabular}{|l|l|l|}
        \hline
        \multicolumn{3}{|l|}{\textbf{Zumbro River, 2003}} \\
        \hline
            & 402m & 804m \\
        \hline
        \multirow{2}{*}{E[Danny]}
            & 0.02922 & 0.007066 \\
            & (0.006786, 0.05994) & (0.0000, 0.03403) \\
        \hline
        \multirow{2}{*}{E[John]}
            & 0.03388 & 0.008312 \\
            & (0.008584, 0.06880) & (0.0000, 0.04188) \\
        \hline
        \multirow{2}{*}{E[Tom]}
            & 0.02228 & 0.012960 \\
            & (0.002430, 0.05385) & (0.0000, 0.05642) \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.81890 & 0.837100 \\
            & (0.749500, 0.88540) & (0.7615, 0.90700) \\
        \hline
        \multirow{2}{*}{p[John]}
            & 0.81770 & 0.852500 \\
            & (0.740100, 0.88670) & (0.7597, 0.92230) \\
        \hline
        \multirow{2}{*}{p[Tom]}
            & 0.73120 & 0.805400 \\
            & (0.625400, 0.82440) & (0.6885, 0.89780) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.66550 & 0.651600 \\
            & (0.549100, 0.78150) & (0.5098, 0.78210) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.29950 & 0.395800 \\
            & (0.236400, 0.36550) & (0.3100, 0.48520) \\
        \hline
    \end{tabular}
    \\

    Again, the 402m data converged well.  With respect to the 804m data, while
    \(\psi\) and \(\theta\) converged really well, none of the other parameters
    did. \\

    \begin{tabular}{|l|l|l|l|}
        \hline
        \multicolumn{2}{|l|}{\textbf{Zumbro River, 2004}} \\
        \hline
            & 402m \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.9166 \\
            & (0.7739, 0.9918) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.4773 \\
            & (0.3586, 0.6114) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.4232 \\
            & (0.3073, 0.5520) \\
        \hline
    \end{tabular}
    \\

    This data converged well.  However, as is the case with all of the 2004
    data, we feel that the absence of E from the model makes the estimates much
    less dependable. \\

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[dvipsnames, table]{xcolor}

\begin{document}

%%% *STANDARD HIERARCHICAL MODEL*:
\section{Standard Hierarchical Model}

    %% MODEL PARAMETERS:
    \subsection{Model Parameters}

    %% SIMULATED DATA, PT. 1:
    \subsection{Simulated Data}

    \noindent{\begin{tabular}{|l|l|l|l|}
        \hline
        \multicolumn{4}{|l|}{\textbf{The Model vs. Simulated Data}} \\
        \hline
            \(\psi\) & \(\theta\) & Convergence & 95\% CI (\(\psi\)) \\
        \hline
        \multirow{5}{*}{0.20}
            & \cellcolor{Green}0.20 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.112, 0.305) \\
            & \cellcolor{Green}0.40 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.142, 0.341) \\
            & \cellcolor{Green}0.60 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.098, 0.284) \\
            & \cellcolor{Green}0.80 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.097, 0.281) \\
            & \cellcolor{Yellow}1.00 & \cellcolor{Yellow}Okay &
              \cellcolor{Yellow}(0.117, 0.302) \\
        \hline
        \multirow{5}{*}{0.40}
            & \cellcolor{Yellow}0.20 & \cellcolor{Yellow}Okay &
              \cellcolor{Yellow}(0.388, 0.721) \\
            & \cellcolor{Green}0.40 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.270, 0.494) \\
            & \cellcolor{Green}0.60 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.287, 0.512) \\
            & \cellcolor{Red}0.80 & \cellcolor{Red}Bad &
              \cellcolor{Red}(0.277, 0.507) \\
            & \cellcolor{Yellow}1.00 & \cellcolor{Yellow}Okay &
              \cellcolor{Yellow}(0.279, 0.503) \\
        \hline
        \multirow{5}{*}{0.60}
            & \cellcolor{Yellow}0.20 & \cellcolor{Yellow}Good &
              \cellcolor{Yellow}(0.312, 0.581) \\
            & \cellcolor{Green}0.40 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.400, 0.630) \\
            & \cellcolor{Yellow}0.60 & \cellcolor{Yellow}Okay &
              \cellcolor{Yellow}(0.462, 0.687) \\
            & \cellcolor{Yellow}0.80 & \cellcolor{Yellow}Okay &
              \cellcolor{Yellow}(0.502, 0.727) \\
            & \cellcolor{Red}1.00 & \cellcolor{Red}Bad &
              \cellcolor{Red}(0.318, 0.549) \\
        \hline
        \multirow{5}{*}{0.80}
            & \cellcolor{Green}0.20 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.578, 0.838) \\
            & \cellcolor{Green}0.40 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.736, 0.915) \\
            & \cellcolor{Yellow}0.60 & \cellcolor{Yellow}Okay &
              \cellcolor{Yellow}(0.587, 0.829) \\
            & \cellcolor{Yellow}0.80 & \cellcolor{Yellow}Okay &
              \cellcolor{Yellow}(0.599, 0.811) \\
            & \cellcolor{Red}1.00 & \cellcolor{Red}Bad &
              \cellcolor{Red}(0.612, 0.830) \\
        \hline
        \multirow{5}{*}{1.00}
            & \cellcolor{Yellow}0.20 & \cellcolor{Yellow}Good &
              \cellcolor{Yellow}(0.895, 0.999) \\
            & \cellcolor{Yellow}0.40 & \cellcolor{Yellow}Okay &
              \cellcolor{Yellow}(0.927, 0.999) \\
            & \cellcolor{Green}0.60 & \cellcolor{Green}Good &
              \cellcolor{Green}(0.949, 1.000) \\
            & \cellcolor{Yellow}0.80 & \cellcolor{Yellow}Good &
              \cellcolor{Yellow}(0.802, 0.954) \\
            & \cellcolor{Red}1.00 & \cellcolor{Red}Bad &
              \cellcolor{Red}(0.800, 0.955) \\
        \hline
    \end{tabular}}

%%% *DISCUSSION*:
\section{Discussion}

    %% GETTING THE ACTUAL DATA TO CONVERGE:
    \subsection{Obtaining Convergence on the Actual Data}
    Recall that our standard hierarchical model contains the following
    parameters: \(\psi\) (the rate of occupancy), \(\theta\) (the probability
    of laying down a track given occupancy), \(p\) (the probability of
    detecting a track given that it is present, which is unique to each
    observer and makes \(1-p\) the false negative rate of detecting a track),
    and \(E\) (the false positive rate of detecting a track, which is unique to
    each observer).

    Once both the standard hierarchical model and the addition of a CAR prior
    distribution on \(\theta\) to the standard model exhibited convergence on
    our simulated data, we moved onto running both models on the data given to
    us by the Minnesota DNR.  Recall that data was gathered during the winters
    of 2003 and 2004 along the Mississippi, Whitewater, and Zumbro Rivers and
    aggregated with ArcGIS into vectors containing ones and zeroes representing
    the detection and non-detection of a track, respectively, within plots of
    length 402 meters, 804 meters, and 1608 meters.  The covariates recorded
    were: the observer, the date, and the number of days since the last snow
    event.  In general, the sparseness of the data gathered in 2004 caused us
    to simplify the model in order to obtain results.  Unfortunately, the
    simplification results in estimates of \(\psi\) that do not seem accurate
    and are not directly comparable to estimates of \(\psi\) on 2003's data.

    The standard model converged reliably on all data gathered in 2003, but it
    did not converge on any of the data gathered in 2004.  Considering that the
    amount of data gathered in 2004 pales in comparison to the amount of data
    gathered in 2003, this result was not surprising.  The vast majority of
    2004's data consists of just one observer taking observations once after
    each snow event, which causes \(p\) and \(E\) in particular to not converge,
    regardless of plot size.

    To obtain convergence on 2004's relatively sparse data, we removed \(E\),
    which adds to the model the assumption that there are no false positives
    and, consequently, simplifies it greatly.  Although the model still did not
    converge on data with plot sizes of 804m and 1608m, both the Whitewater and
    Zumbro Rivers' data at the 402m plot size converged.  Although none of the
    Mississippi River's 2004 data converged, we still include estimates of
    \(p\), \(\psi\), and \(\theta\) at the 402m plot size to accompany the
    estimates corresponding to the Whitewater and Zumbro Rivers.  For the most
    part, however, we feel that the absence of \(E\) from the model makes the
    the estimates of \(\psi\) much less dependable.

    The addition of a CAR prior distribution on \(\theta\) to the standard model
    caused the model to fail to converge on all of the data.  Although the
    standard model and the CAR model performed similarly on simulated data
    whenever both models converged, the standard model converged much more often
    than did the CAR model.  This is most likely due to the fact that the CAR
    model attempts to estimate too many parameters.  Whereas the standard model
    estimates between eight and twelve parameters on the actual data (\(\psi\),
    \(\theta\), the four parameters of the beta distributions corresponding to
    \(p\) and \(E\), \(p\) for each observer, and \(E\) for each observer), the
    CAR model estimates \(\theta\) for each site.  Because there are at least
    thirty-five sites in each data set (regardless of plot size), the CAR prior
    distribution adds a considerable amount of complexity to the model.

    We also tried to simplify this model by eliminating \(E\) because this was
    somewhat successful with respect to convergence with the standard model.
    We first attempted to fit this model to data from 2003 at the 402m plot
    size.  Although the model successfully converged on all of this data, its
    estimates of \(\psi\), all of which were greater than 0.9, did not seem
    reasonable, especially in comparison to the standard model's estimates when
    given the same data.  As a result, we did not attempt to fit this model to
    the rest of the data and do not include this model's estimates within our
    results.

    %% RESULTS:
    \subsection{Results}
    Below, in tables, lie our estimates for all of the Minnesota DNR's data from
    2003 and 2004.  Below each table is detailed commentary about the ability of
    the standard hierarchical model to convergence to the corresponding data. \\

    % Mississippi River!
    \noindent{\begin{tabular}{|l|l|l|l|}
        \hline
        \multicolumn{4}{|l|}{\textbf{Mississippi River, 2003}} \\
        \hline
            & 402m & 804m & 1608m \\
        \hline
        \multirow{2}{*}{E[Danny]}
            & 0.01954 & 0.04808 & 0.06885 \\
            & (0.006515, 0.03663) & (0.01874, 0.08187) & (0.01778, 0.1383) \\
        \hline
        \multirow{2}{*}{E[John]}
            & 0.05216 & 0.07771 & 0.13650 \\
            & (0.027710, 0.07745) & (0.03881, 0.12100) & (0.03449, 0.2330) \\
        \hline
        \multirow{2}{*}{E[Tom]}
            & 0.02668 & 0.06140 & 0.10230 \\
            & (0.011990, 0.04622) & (0.02789, 0.10390) & (0.04287, 0.1796) \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.65240 & 0.67340 & 0.74960 \\
            & (0.548300, 0.75990) & (0.56760, 0.78290) & (0.60510, 0.8910) \\
        \hline
        \multirow{2}{*}{p[John]}
            & 0.67770 & 0.77580 & 0.82540 \\
            & (0.583500, 0.77280) & (0.66060, 0.88690) & (0.71390, 0.9326) \\
        \hline
        \multirow{2}{*}{p[Tom]}
            & 0.53670 & 0.54220 & 0.65330 \\
            & (0.501200, 0.61300) & (0.50160, 0.62850) & (0.51530, 0.8104) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.59380 & 0.69370 & 0.75820 \\
            & (0.439000, 0.75990) & (0.51800, 0.87380) & (0.54110, 0.9300) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.15280 & 0.20730 & 0.27690 \\
            & (0.111900, 0.19780) & (0.14580, 0.27390) & (0.19030, 0.3716) \\
        \hline
    \end{tabular}}
    \\

    This data converged well at the 402m and 804m plot sizes.  At the 1608m plot
    size, \(E\), \(\psi\), and \(\theta\) did not converge well. \\

    \noindent{\begin{tabular}{|l|l|}
        \hline
        \multicolumn{2}{|l|}{\textbf{Mississippi River, 2004}} \\
        \hline
            & 402m \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.3129 \\
            & (0.2174, 0.8107) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.7613 \\
            & (0.6609, 0.8833) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.8511 \\
            & (0.2426, 0.9973) \\
        \hline
    \end{tabular}}
    \\

@@

    % Whitewater River!
    \noindent{\begin{tabular}{|l|l|l|}
        \hline
        \multicolumn{3}{|l|}{\textbf{Whitewater River, 2003}} \\
        \hline
            & 402m & 804m \\
        \hline
        \multirow{2}{*}{E[Danny]}
            & 0.05608 & 0.0555 \\
            & (0.02474, 0.09554) & (0.002859, 0.1390) \\
        \hline
        \multirow{2}{*}{E[John]}
            & 0.16570 & 0.1931 \\
            & (0.10130, 0.23510) & (0.065910, 0.3384) \\
        \hline
        \multirow{2}{*}{E[Tom]}
            & 0.15350 & 0.2241 \\
            & (0.09758, 0.21660) & (0.110000, 0.3623) \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.66990 & 0.6985 \\
            & (0.56080, 0.79040) & (0.573100, 0.8366) \\
        \hline
        \multirow{2}{*}{p[John]}
            & 0.92040 & 0.9877 \\
            & (0.84270, 0.97590) & (0.945100, 1.0000) \\
        \hline
        \multirow{2}{*}{p[Tom]}
            & 0.75910 & 0.8575 \\
            & (0.65060, 0.85800) & (0.745400, 0.9600) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.87590 & 0.9126 \\
            & (0.72910, 0.98880) & (0.746900, 0.9955) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.24100 & 0.3779 \\
            & (0.17890, 0.30900) & (0.286500, 0.4721) \\
        \hline
    \end{tabular}}
    \\

    While the 402m data converged well, \(E\), \(\psi\), and \(\theta\) did not
    converge well for the 804m data. \\

    \noindent{\begin{tabular}{|l|l|l|l|}
        \hline
        \multicolumn{2}{|l|}{\textbf{Whitewater River, 2004}} \\
        \hline
            & 402m \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.8237 \\
            & (0.5323, 0.9804) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.6066 \\
            & (0.4246, 0.8382) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.2068 \\
            & (0.1211, 0.3550) \\
        \hline
    \end{tabular}}
    \\

    This data converged well.  However, we feel that the absence of \(E\) from
    the model makes the estimates much less dependable.  The estimates are also
    much less precise than those from 2003 -- the confidence intervals of
    \(\psi\) and of \(p[Danny]\) are twice as large as those from 2003. \\

    % Zumbro River!
    \noindent{\begin{tabular}{|l|l|l|}
        \hline
        \multicolumn{3}{|l|}{\textbf{Zumbro River, 2003}} \\
        \hline
            & 402m & 804m \\
        \hline
        \multirow{2}{*}{E[Danny]}
            & 0.02922 & 0.007066 \\
            & (0.006786, 0.05994) & (0.0000, 0.03403) \\
        \hline
        \multirow{2}{*}{E[John]}
            & 0.03388 & 0.008312 \\
            & (0.008584, 0.06880) & (0.0000, 0.04188) \\
        \hline
        \multirow{2}{*}{E[Tom]}
            & 0.02228 & 0.012960 \\
            & (0.002430, 0.05385) & (0.0000, 0.05642) \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.81890 & 0.837100 \\
            & (0.749500, 0.88540) & (0.7615, 0.90700) \\
        \hline
        \multirow{2}{*}{p[John]}
            & 0.81770 & 0.852500 \\
            & (0.740100, 0.88670) & (0.7597, 0.92230) \\
        \hline
        \multirow{2}{*}{p[Tom]}
            & 0.73120 & 0.805400 \\
            & (0.625400, 0.82440) & (0.6885, 0.89780) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.66550 & 0.651600 \\
            & (0.549100, 0.78150) & (0.5098, 0.78210) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.29950 & 0.395800 \\
            & (0.236400, 0.36550) & (0.3100, 0.48520) \\
        \hline
    \end{tabular}}
    \\

    Again, the 402m data converged well.  With respect to the 804m data, while
    \(\psi\) and \(\theta\) converged well, none of the other parameters did. \\

    \noindent{\begin{tabular}{|l|l|l|l|}
        \hline
        \multicolumn{2}{|l|}{\textbf{Zumbro River, 2004}} \\
        \hline
            & 402m \\
        \hline
        \multirow{2}{*}{p[Danny]}
            & 0.9166 \\
            & (0.7739, 0.9918) \\
        \hline
        \multirow{2}{*}{\(\psi\)}
            & 0.4773 \\
            & (0.3586, 0.6114) \\
        \hline
        \multirow{2}{*}{\(\theta\)}
            & 0.4232 \\
            & (0.3073, 0.5520) \\
        \hline
    \end{tabular}}
    \\

    This data converged well.  However, as is the case with all of the 2004
    data, we feel that the absence of \(E\) from the model makes the estimates
    much less dependable.

    %%
    \subsection{The Effect of Plot Size}
    %%
    \subsection{All Plots vs. Every Other Plot}
    %%
    \subsection{How Important Are Our Covariates?}
    %%
    \subsection{Best Practices for Measuring Otter Occupancy}
